Stool Microbiome Analysis

### 2021-12-01 Rmarkdown/analysis/Fecal_Microbiome_TMAO_Analysis_211105.Rmd
Look at christensenellaceae genus with BMI

Merge phenotype and microbiome data for linear regression analysis
```{r}
phen <- merge(phen, otuData_desRes, by=0)
rownames(phen) <- phen[,"Row.names"]
phen <- subset(phen, select = -c(Row.names))
```

@@

>>>>

Merge phenotype and microbiome data for linear regression analysis
```{r Merge pheno and microbiome tertile DESeq results}
phen <- merge(phen, otuData_desRes, by=0)
rownames(phen) <- phen[,"Row.names"]
phen <- subset(phen, select = -c(Row.names))
```

@@

The family christensenellaceae is widely inversely associated with BMI. A review is [here](https://bmcbiol.biomedcentral.com/articles/10.1186/s12915-019-0699-4).

```{r Christensenellaceae genus and BMI}
summary(lm(f__Christensenellaceae_g__ ~ bmi_final + sex + age, phen))
```
